Verifying Demonstrations

### 2016-04-19 PPProtestAuth-content.tex
Adds slides target
The slides structure is taken from the 30% seminar, so it's the same
theme and structure.
There is no longer any \ackname in llncs
Adds comments from meetings with Sébastien

\title{Authenticating Protests}
\author{%
  Daniel Bosk\inst{1}
  \and
  Sébastien Gambs\inst{2}
  \and
  Sonja Buchegger\inst{1}
}
\institute{%
  School of Computer Science and Communication\\
  KTH Royal Institute of Technology, Stockholm\\
  \texttt{\{dbosk,buc\}@kth.se}
  \and
  Université de Rennes 1 and Inria, Rennes\\
  \texttt{sgambs@irisa.fr}
}

@@

@@

\section{Adapting PROPS}

@@

\subsubsection*{\ackname}

>>>>

\title{%
  Verifying Demonstrations
}
\author[D.~Bosk et al.]{%
  Daniel Bosk\inst{1}
  \and
  Sébastien Gambs\inst{2}
  \and
  Sonja Buchegger\inst{1}
}
\institute[KTH, UQAM]{%
  School of Computer Science and Communication\\
  KTH Royal Institute of Technology, Stockholm\\
  \texttt{\{dbosk,buc\}@kth.se}
  \and
  Université de Quebec à Montreal\\
  \texttt{sgambs@uqam.ca}
}

@@

\mode*

@@

\subsection{The Problem}

Usually the count by the organizers and count by police differs, we want to 
solve this problem.

We can divide the problem into three parts:
\begin{itemize}
  \item Register participants in the system.
  \item Collect the necessary data.
  \item Perform the counting and verification.
\end{itemize}

To register the participants we might be able to piggy-back on existing 
\acp{PKI} and blind signatures --- similarly as for voting systems.

We have the verifiability properties in voting:
\begin{description}
  \item[Individual] Individual verifiability allows a voter to verify her own 
    vote was included in the election outcome.
  \item[Universal] Universal verifiability allows voters or observers to check 
    that the election outcome corresponds to the votes cast.
  \item[Eligibility] Eligibility verifiability allows voters and observers to 
    check that each vote in the election outcome was cast by a uniquely 
    registered voter.
\end{description}

\section{Adapting PROPS}
\label{AdaptingPROPS}

@@

\section{System Model}
\label{SystemModel}

The model will be a public anonymous blackboard.
We will use this blackboard to publish locations proofs after the protest.

We want the following properties:
\begin{description}
  \item[Correctness] We want to count everyone once and only once.
  \item[Unforgeability] Participation should not be possible to forge.
    I.e.\ non-participants should not be able to say they were present.
    This together with correctness will provide authenticity to the protest 
    verification.
  \item[Anonymity] Given the data published on the blackboard, the adversary 
    should not be able to tell two participants apart.
  \item[Decentralized] There should be no central authority.
\end{description}

Can the adversary publish a public-key looking random string to sabotage the 
blackboard?

Basically the properties that we are interested in are similar to those of 
electronic voting, so we would like to reuse as many definitions from there as 
possible.

\subsection{Decentralization}

In \ac{PROPS} the prover must have a secret signed by \iac{CA}.
This \ac{CA} can be implemented as a secret-sharing scheme.
Usually these have a fixed threshold \((t, n)\).
This can be achieved by commitments, then the shared secret is computed.
However, it would be interesting to have the threshold dynamically adapt to the 
number of participants, i.e.\ participants can join later too.

Can the adversary then \enquote{join} enough many to throw off the threshold?

\subsection{Correctness and Unforgeability}

Each prover must reach a threshold of witnesses \(k\).
We must be able to prevent a prover to collect \(2k\) witnesses and then 
publishing two proofs.
We therefore must achieve conditional linkability between the \acp{LP} 
published on the blackboard.
If a second \ac{LP} for a secret is published, then those should be linkable.
This might be possible to achieve with unique group 
signatures~\cite{UniqueGroupSignatures,UniqueRingSignatures,ListSignatures}.

\section{Useful Primitives}
\label{UsefulPrimitives}

\dots

\subsubsection*{Acknowledgements}
